On Extending a Full-Sharing Design with Batched Scheduling

### 2015-04-15 paper.tex
introduction -> end

Multithreading in Prolog is the ability to concurrently perform
computations, in which each computation runs independently but shares
the program clauses. When multithreading is combined with tabling, we
have the best of both worlds, since we can exploit the combination of
higher procedural control with higher declarative semantics. To the
best of our knowledge, XSB~\cite{Marques-08} and Yap~\cite{Areias-12a}
were the only Prolog systems that were able to combine both
multithreading with tabling. Yap's threads have their own execution
stacks and only share the code area where predicates, records, flags
and other global non-backtrackable data are stored. For tabled
evaluation, a thread views its tables as private but, at the engine
level, Yap has three designs: (i) The {\bf No-Sharing (NS)} design,
where each thread allocates fully private tables for each new tabled
subgoal called during its computation. (ii) {\bf Subgoal-Sharing
  (SS)}, where threads share part of the table space and the (iii)
{\bf Full-Sharing (FS)}, where threads share the complete table
space.

>>>>

Multithreading in Prolog is the ability to concurrently perform
computations, in which each computation runs independently but shares
the program clauses. When multithreading is combined with tabling, we
have the best of both worlds, since we can exploit the combination of
higher procedural control with higher declarative semantics. To the
best of our knowledge, XSB~\cite{Marques-08} and Yap~\cite{Areias-12a}
were the only Prolog systems that were able to combine both
multithreading with tabling. Yap's threads have their own execution
stacks and only share the code area where predicates, records, flags
and other global non-backtrackable data are stored. For tabled
evaluation, a thread views its tables as private but, at the engine
level, Yap has three designs: (i) The {\bf No-Sharing (NS)} design,
where each thread allocates fully private tables for each new tabled
subgoal called during its computation. (ii) The {\bf Subgoal-Sharing
  (SS)}, where threads share part of the table space and the (iii) The
{\bf Full-Sharing (FS)}, where threads share the complete table space.
